### 2018-07-30 manuscript.rmd
ran physigs, model fitting w/ new phylo

```{r load_trees, include=F}
#Load tree
rRNA18S = read.nexus('bipartitions_root.boot10')
transcriptome = read.tree('ultimatephylo2018.tre')
#plot.phylo(consensus)
#is.rooted(consensus)
#nodelabels()
rRNA18S = reroot(rRNA18S, 76, 0.001)
rRNA18S$tip.label = str_replace_all(rRNA18S$tip.label,'_',' ')
rRNA18S$tip.label[rRNA18S$tip.label=="Cordagalma cordiforme"] = "Cordagalma ordinatum"
rRNA18S$tip.label[rRNA18S$tip.label=="Cordagalma sp "] = "Cordagalma ordinatum"
rRNA18S$tip.label[rRNA18S$tip.label=="Clausophyes ovata"] = "Kephyes ovata"
rRNA18S$tip.label[rRNA18S$tip.label=="Erenna sp"] = "Erenna sirena"
rRNA18S$tip.label[rRNA18S$tip.label=="Apolemia sp"] = "Apolemia lanosa"
rRNA18S$tip.label[rRNA18S$tip.label=="Apolemia sp "] = "Apolemia rubriversa"
rRNA18S$tip.label[rRNA18S$tip.label=="Sphaeronectes gracilis"] = "Sphaeronectes koellikeri"
rRNA18S$tip.label[rRNA18S$tip.label=="Prayidae D27SS7"] = "Desmophyes haematogaster"
rRNA18S$tip.label[rRNA18S$tip.label=="Prayidae D27D2"] = "Craseoa lathetica"
rRNA18S = drop.tip(rRNA18S, 41:42) #drop outgroups
rRNA18S = drop.tip(rRNA18S, c(16,31,23,24)) #drop Cordagalma, Clausophyid, Nectopyramis, Nectadamas
#plot(rRNA18S)

transcriptome$tip.label = str_replace_all(transcriptome$tip.label,'_',' ')
transcriptome$tip.label[transcriptome$tip.label=="Cordagalma sp"] = "Cordagalma ordinatum"
transcriptome$tip.label[transcriptome$tip.label=="Prayidae D27SS7"] = "Desmophyes haematogaster"
transcriptome$tip.label[transcriptome$tip.label=="Prayidae D27D2"] = "Craseoa lathetica"
transcriptome = reroot(transcriptome, 22, 0.001)
transcriptome = drop.tip(transcriptome, 19:26) #drop outgroups
#plot(transcriptome)

multitree = list(rRNA18S,transcriptome)
class(multitree)="multiPhylo"
STree = superTree(multitree, rooted = T, method = "MRP", start = transcriptome)
consensus = STree[[2]]
consensus = drop.tip(consensus, "Physonect sp ")
consensus = drop.tip(consensus, "Erenna sirena")
consensus$tip.label[consensus$tip.label=="Physophora gilmeri"] = "Physophora h" ### ARTIFIIAL SUBSTITUTION ###
consensus = drop.tip(consensus, "Physophora hydrostatica")
consensus$tip.label[consensus$tip.label=="Physophora h"] = "Physophora hydrostatica"
consensus$tip.label[consensus$tip.label=="Vogtia pentacantha"] = "Vogtia serrata"
consensus = drop.tip(consensus, "Rosacea flaccida")
#plot(consensus)

@@

1.05 Plate with all the tentillum diversity.
1.1 Table showing each character’s (illustrating the character per row)  the phylogenetic signal K with the p-value obtained by testing against 1000 simulated permutations, and the number of species included.
```{r phylosignals}
phylosignals = as.data.frame(matrix(ncol=3, nrow=ncol(sharedmean_logs[,-1])))
names(phylosignals) = c("K", "P", "Ntaxa")
for(i in 2:ncol(sharedmean_logs)){
  CH_I=as.numeric(sharedmean_logs[,i])
  names(CH_I) = rownames(sharedmean_logs)
  SE_I = as.numeric(castSE[,i])
  names(SE_I) = castSE$Species
  CH_I= CH_I[!is.na(CH_I)]
  SE_I= SE_I[!is.na(SE_I)]
  SE_I = SE_I[which(names(SE_I)%in%names(CH_I))]
  CH_I = CH_I[which(names(CH_I)%in%names(SE_I))]
  treeI = drop.tip(ultram,which(!(ultram$tip.label %in% names(CH_I))))
  class(treeI) = "phylo"
  #print(names(sharedmeans)[i]);print(phylosig(treeI, CH_I, se = SE_I, test=T) %>% .[c("K","P")])
  rownames(phylosignals)[i-1] <- names(sharedmean_logs)[i]
  PSIG <- phylosig(treeI, CH_I, se = SE_I, test=T)
  phylosignals[i-1,1] <- PSIG$K
  phylosignals[i-1,2] <- PSIG$P
  phylosignals[i-1,3] <- length(CH_I)
}
write.csv(phylosignals, "PhylosignalsWSE_log.csv")
```

@@

#Model adequacy
  worthy_models = AICdf[which(AICdf$white_noise != 0 & AICdf$starBM != 0),]
  MAD = as.data.frame(matrix(ncol = 6, nrow = nrow(worthy_models)))
  names(MAD) = c("msig", "cvar", "svar", "sasr", "shgt", "dcfd")
  rownames(MAD) = worthy_models$Variable
  for(m in 1:nrow(worthy_models)){
    C = Q_sharedmean_logs[,which(names(Q_sharedmean_logs) == worthy_models$Variable[m])]
    names(C) = rownames(Q_sharedmean_logs)
    C = C[!is.na(C)]
    Ctree = drop.tip(ultram, which(!(ultram$tip.label %in% names(C))))
    C = C[match(Ctree$tip.label, names(C))]
    class(Ctree)="phylo"
    FC <- fitContinuous(Ctree,C,model=worthy_models$Best_model[m])
    UTC <- make_unit_tree(FC)
    picstat_data <- calculate_pic_stat(UTC)
    sim <- simulate_char_unit(UTC)
    picstat_sim <- calculate_pic_stat(sim)
    compare_pic_stat(picstat_data, picstat_sim) %>% .$p.values -> MAD[m,]
  }
  phy_models = data.frame(worthy_models,MAD)
  phy_models[,8:13] = apply(phy_models[,8:13], 2,round3)
```
1.3 Figure showing major categorical character shifts, gains, and losses on a simplified phylogeny.

>>>>

```{r load_tree, include=F}
#Load tree
consensus = ape::read.tree("concatenate.fasta.treefile")
consensus = reroot(consensus,99)
consensus = drop.tip(consensus, c(56:61))
consensus$tip.label = str_replace_all(consensus$tip.label,"_"," ")

@@

1.05 Plate with all the tentillum diversity.
1.1 Table showing each character’s (illustrating the character per row)  the phylogenetic signal K with the p-value obtained by testing against 1000 simulated permutations, and the number of species included.
```{r phylosignals}
phylosignals = as.data.frame(matrix(ncol=3, nrow=ncol(sharedmean_logs[,-1])))
names(phylosignals) = c("K", "P", "Ntaxa")
for(i in 2:ncol(sharedmean_logs)){
  CH_I=as.numeric(sharedmean_logs[,i])
  names(CH_I) = sharedmean_logs$Species
  SE_I = as.numeric(castSE[,i])
  names(SE_I) = castSE$Species
  CH_I= CH_I[!is.na(CH_I)]
  SE_I= SE_I[!is.na(SE_I)]
  SE_I = SE_I[which(names(SE_I)%in%names(CH_I))]
  CH_I = CH_I[which(names(CH_I)%in%names(SE_I))]
  treeI = drop.tip(ultram,which(!(ultram$tip.label %in% names(CH_I))))
  class(treeI) = "phylo"
  #print(names(sharedmeans)[i]);print(phylosig(treeI, CH_I, se = SE_I, test=T) %>% .[c("K","P")])
  rownames(phylosignals)[i-1] <- names(sharedmean_logs)[i]
  PSIG <- phylosig(treeI, CH_I, se = SE_I, test=T)
  phylosignals[i-1,1] <- PSIG$K
  phylosignals[i-1,2] <- PSIG$P
  phylosignals[i-1,3] <- length(CH_I)
  phylosignals$K = round(phylosignals$K,3)
}
write.csv(phylosignals, "PhylosignalsWSE_log.csv")
```

@@

#Model adequacy
  worthy_models = AICdf[which(AICdf$white_noise != 0 & AICdf$starBM != 0),]
  MAD = as.data.frame(matrix(ncol = 6, nrow = nrow(worthy_models)))
  names(MAD) = c("msig", "cvar", "svar", "sasr", "shgt", "dcfd")
  rownames(MAD) = worthy_models$Variable
  for(m in 1:nrow(worthy_models)){
    C = Q_sharedmean_logs[,which(names(Q_sharedmean_logs) == worthy_models$Variable[m])]
    names(C) = rownames(Q_sharedmean_logs)
    C = C[!is.na(C)]
    Ctree = drop.tip(ultram, which(!(ultram$tip.label %in% names(C))))
    C = C[match(Ctree$tip.label, names(C))]
    class(Ctree)="phylo"
    FC <- fitContinuous(Ctree,C,model=worthy_models$Best_model[m])
    UTC <- make_unit_tree(FC)
    picstat_data <- calculate_pic_stat(UTC)
    sim <- simulate_char_unit(UTC)
    picstat_sim <- calculate_pic_stat(sim)
    compare_pic_stat(picstat_data, picstat_sim) %>% .$p.values -> MAD[m,]
  }
  phy_models = data.frame(worthy_models,MAD)
  phy_models[,7:12] = apply(phy_models[,7:12], 2,round3)
```
1.3 Figure showing major categorical character shifts, gains, and losses on a simplified phylogeny.
